\documentclass{article}
\usepackage{fullpage}
\usepackage{url}
\usepackage[draft,inline,nomargin,index]{fixme} 

\title{CS 6480: Advanced Computer Networks - Fall 2015}
\author{Homework Assignment: 0\\
About you and the course...
} 
\date{}

\begin{document}
\maketitle

\section*{Answer the following questions}

\begin{enumerate}

\item Where did you grow up? (Country, state, town.) - India, Maharastra, Pune

\item Which high school did you graduate from? - Abhinav Vidyalaya Highschool

\item What has been your most significant achievement to date? - Raised to position of Software Architect in Deloitte.

\item Where do you see yourself career wise in five years' time? - Completing my PhD.

\item And in ten years? - doing more research as scientist with research lab or as a professor with some university or may be as a high school teacher in India - teaching in a practical way and challenging thinking of students, rather than bookish - the way which I missed

\item Why did you decide to study at the University of Utah? - University of Utah has the best research going among the universities where I got the admit.

\item What made you decide to study Computer Science? - I like it.

\item Which CS course has been most meaningful so far? Why? - Security. Its exciting.

\item Did you take an undergraduate course in networking? If, so,
what textbook did you use and what was your final grade? - Yes, referred "Computer Networks by Tanenbaum". Grade was A. 

\item If you are a masters student, which option (thesis, project, course)
are you planning to do? Why? -Thesis. I would like to continue as PhD student.

\item What is your GPA? - Undergraduate GPA is approx 3.4 

\item Read the CS 6480 syllabus. Do you have any concerns? If so, please
list them here and/or follow up with the instructor (sooner rather than
later). - After completing course, will I be able to design working SDN or network for cloud ?

\item What have you heard ``from the grapevine'' about CS 6480 that you are
concerned about? - I completed my under graduation 9 years ago and was not into networking since then. So I need to brush up "existing" knowledge and then further toil for this "research oriented" course. So I am  mentally prepared for tough challenge. 

\item What have you heard ``from the grapevine'' about CS 6480 that you are
looking forward to? - Labs / Projects in this course are based on real life research scenarios. Looking forward for the opportunity.

\item What do you expect to get out of CS 6480? (List at least three.)
\begin{enumerate}
\item My undergraduate course was more theoretical. Hands on programming was limited to Socket programming. So expecting to gain more hands on experience on different flavors of networking.
\item Insight into latest developments/research in computer networking and possibly finding out some topic for thesis.
\item Expecting this "core" course will help me have better understanding of CS.

\end{enumerate}
\end{enumerate}

\end{document}