\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{epsfig,xspace,url}
\usepackage{authblk}


\title{CS 6480: Class discussion summary\\
HA 2.b\\}
\author{Damodar Sahasrabudhe}
\affil{School of Computing, University of Utah}

\begin{document}

\maketitle
\section*{Discussion summary}

\begin{itemize}

\item {\it Summary:} 
\begin{itemize}
\item Nothing but controller of OpenFlow
\item OS analogy is limited. OS is generalized for all kinds of programs. NOX targets apps specific for network management.
\item Though better controllers are available now, NOX was the first such concept suggested.

\end{itemize} 

\item {\it Strengths:} 
\begin{itemize}
\item This is the first paper which suggested sophisticated controller. So in spite of some loopholes, it is first such idea of the kind. 
\end{itemize}

\item {\it Weakness:} 
\begin{itemize}
\item No performance measures given. As system is running, they could have given performance measures.
\item level of abstraction may not be sufficient.
\end{itemize}


\item {\it Connection with other work:} 
A brief mention of Ethan\cite{Ethane}.

\item {\it Future work:} 
\begin{itemize}
\item When implemented at large scale such as internet, Controller can not view each and every undelivered packet. System should be intelligent enough to handle such scenarios

\end{itemize}

\end{itemize}

\begin{thebibliography}{1}
\bibitem{Ethane} Martin Casado, Michael J. Freedman, Justin Pettit,Jianying Luo, Nick McKeown, Scott Shenker. "Ethane: Taking Control of the Enterprise"

\end{thebibliography}

\end{document}



